\begin{rSection}{Work Experience}
  % ftd
  \begin{job}{DevOps Engineering Intern}{May 2022 - Present}{FTD Solutions}{}
    \item Collaborated with a software development team to design and build an automated workflow system.
    % \item Designed workflows for FTD and its clients in this brand-new platform.
    \item Designed, implemented, and integrated a new database for the company.
    \item Wrote {\bf Python} script to transfer company forms from {\bf JSON} to {\bf XML}: \href{https://github.com/MatousAc/orbify}{github.com/MatousAc/orbify}
  \end{job}

  % tutor
  \begin{job}{Computer Science Tutor/Lab Operator}{Aug. 2020 - Dec. 2022}{Southern Adventist University}{Collegedale, TN}{}
    \item Helped students with their {\bf Microsoft Office} and {\bf HgTML5} homework.
    \item Tutored students in procedural programming and basic algorithms using {\bf Java}.
  \end{job}

  % ornl
  \begin{job}{Physics Intern}{Jan. 2022}{Oak Ridge National Laboratory}{Oak Ridge, TN}
    \item Diagnosed and monitored an ultra-high vacuum particle beamline.
    %  \item Set up a procedure for gold plating sensitive piping in beamline.
  \end{job}

  % it is written
  \begin{job}{Web Development Intern}{May - Aug. 2020}{It Is Written Inc.}{Collegedale, TN}
    \item Created website for kids, \href{https://buriedtreasure.fun/}{buriedtreasure.fun}, using {\bf Drupal 8}.
    \item Designed, implemented, and integrated features for \href{https://itiswritten.tv}{itiswritten.tv} in {\bf Ruby on Rails}.
  \end{job}
\end{rSection}
